Multi-level Selective Deduplication for VM Snapshots in Cloud Storage

### 2012-03-10 vm_snapshot_sim/2012abs.tex
small adjustment

\begin{abstract}
%Virtualization has became the engine behind many cloud computing platforms.
In a virtualized cloud computing environment, frequent  snapshot backup of virtual disks improves
hosting  reliability while  storage demand of such operations is huge.
A dirtybit-based technique can identify unmodified data between versions 
and full deduplication with fingerprint comparison  can remove more redundant content
while it requires more computing resource.
%with  for similarity comparison and   reliability handling.
%Current snapshot deduplication is mainly done through copy-on-write 
%on fixed-size disk blocks. Such solutions cannot handle the
% cross VM data duplication because VMs do not share any data. 
%In addition, storing VM images and their snapshots
%in the same storage engine reduce the underline design flexibility because 
%these two kinds of data have distinct access requirements.
%In this paper, 
%we show that there is a large amount of duplicated data shared amongy virtual machines
%through a production VM data study and thus it is expective to perform cross-machine deduplication. 
This paper presents a multi-level selective deduplication  scheme which
integrates  inner-VM and cross-VM duplicate elimination under
a stringent resource requirement.
% minimal  resource impact to the existing cloud services.  
This scheme uses popular common data to facilitate 
fingerprint comparison while reducing the cost and it
strikes a balance  between local and global deduplication 
to  increase parallelism and  improve reliability. 
% first perform a large scale study in production VM clusters 
%to show that cross VM data duplication is severe due to they have large amount of
%common data. Then our data analysis finds out that the overall data duplication pattern follows the Zipf's law.
%Base on these discoveries, we propose a snapshot storage deduplication scheme using variable-size chunking
%to address the above problem efficiently.
%We eliminate the majority of cross VM data duplication by pre-select
%a small set of frequently seen data blocks to be shared globally, and we also remove
%many cross snapshot duplication by using smaller chunking granuarity and locality.
Experimental results  show the proposed scheme  can achieve high deduplication ratio while using
a  small  amount of cloud resources. 
\end{abstract}

>>>>

\begin{abstract}
%Virtualization has became the engine behind many cloud computing platforms.
In a virtualized cloud computing environment, frequent  snapshot backup of virtual disks improves
hosting  reliability but storage demand of such operations is huge.
While dirtybit-based technique can identify unmodified data between versions, 
full deduplication with fingerprint comparison  can remove more redundant content
at the cost of computing resources.
%with  for similarity comparison and   reliability handling.
%Current snapshot deduplication is mainly done through copy-on-write 
%on fixed-size disk blocks. Such solutions cannot handle the
% cross VM data duplication because VMs do not share any data. 
%In addition, storing VM images and their snapshots
%in the same storage engine reduce the underline design flexibility because 
%these two kinds of data have distinct access requirements.
%In this paper, 
%we show that there is a large amount of duplicated data shared amongy virtual machines
%through a production VM data study and thus it is expective to perform cross-machine deduplication. 
This paper presents a multi-level selective deduplication  scheme which
integrates  inner-VM and cross-VM duplicate elimination under
a stringent resource requirement.
% minimal  resource impact to the existing cloud services.  
This scheme uses popular common data to facilitate 
fingerprint comparison while reducing the cost and it
strikes a balance  between local and global deduplication 
to  increase parallelism and  improve reliability. 
% first perform a large scale study in production VM clusters 
%to show that cross VM data duplication is severe due to they have large amount of
%common data. Then our data analysis finds out that the overall data duplication pattern follows the Zipf's law.
%Base on these discoveries, we propose a snapshot storage deduplication scheme using variable-size chunking
%to address the above problem efficiently.
%We eliminate the majority of cross VM data duplication by pre-select
%a small set of frequently seen data blocks to be shared globally, and we also remove
%many cross snapshot duplication by using smaller chunking granuarity and locality.
Experimental results  show the proposed scheme  can achieve high deduplication ratio while using
a  small  amount of cloud resources. 
\end{abstract}

### 2012-03-10 vm_snapshot_sim/2012arch.tex
small adjustment

\begin{figure}[htbp]
  \centering
  %\epsfig{file=images/arch.eps, height=2in, width=2.66in}
  \epsfig{file=images/arch.eps, width=3.5in}
  \caption{Snapshot backup architecture of each node.}
  \label{fig:arch}
\end{figure}

@@

%\begin{figure}[htbp]
%  \centering
%  %\epsfig{file=images/dedup_process.eps, height=2in, width=2.66in}
%  \epsfig{file=images/dedup_process.eps,  width=3.2in}
%  \caption{An example  of multi-level deduplication process.}
%  \label{fig:arch}
%\end{figure}
\begin{figure}[htbp]
  \centering
  %\epsfig{file=images/dedup_process.eps, height=2in, width=2.66in}
  \epsfig{file=images/snapshot_representation.eps,  width=3.2in}
  \caption{An example of snapshot representation.}
  \label{fig:snapshot}
\end{figure}

@@

In Aliyun's VM cloud, each VM explicitly maintains  one OS disk, plus one or more data disks.
During VM's creation, its OS disk is directly copied from user's chosen base image.
Given the separation of OS disks and data disks, we study  their characteristics separately.
We expect that data related to OS and popular software installations are not frequently
modified or deleted, to facilitate analysis we call them \emph{OS-related} data, 
and the rest of data, either from OS or data disks, are called \emph{user-related} data.
%base image data as a hint.Through users may change configurations, install software, or write user data into OS disk,
%Thus most of content blocks for the OS related snapshots  shall keep unchanged.
%This is verified in  Section~\ref{sect:exper}.
We have studied the popularity of common blocks in the OS and data disks from a dataset
containing over 1,000 VMs, taking their first snapshots to watch the cross-VM duplication pattern.
Figure \ref{fig:zipf-data} shows the duplicate count for unique data blocks sorted by their ranking in 
terms of the duplication count. $Y$ axis is the popularity of a data block in a log scale 
measured its duplicate count among snapshots. $X$ axis is the identification of data blocks in a log scale
sorted by their duplicate rank.  The rank number 1 is the block with the highest number of duplicates.
These two curves exhibit that the popularity of common blocks partially follows a Zipf-like distribution.
%$Y$ axis is the popularity of an OS block in a log scale 
%measured its duplicate count among snapshots. $X$ axis is the identification of OS blocks in a log scale
%sorted by their duplicate rank.  
%For the top ranked blocks, there is a flat line in terms of duplicate counts. That
%is because there are a large number of OS blocks which have appeared in all copies of such OS releases.

\begin{figure}[htbp]
\centering
\epsfig{file=images/vector.eps, width=3.2in}
%\epsfig{file=images/log-log.disk.eps, width=3in}

@@

%%Our deduplication process is divided into three levels, at each level, we eliminate the most of duplicate data with available knowledge, preventing them from going further because deduplication at deeper level is more expensive.
%
\begin{figure}
  \centering
  \epsfig{file=images/dedup_flow1.eps, height=2in, width=3.5in}
  \caption{Illustration of snapshot deduplication dataflow.}
  \label{fig:dedupflow}
\end{figure}

We illustrate the steps of 3-level deduplication in Figure~\ref{fig:dedupflow}, which can be summarized as 5 steps:
\begin{enumerate}
\item {\em Segment level checkup.}
As shown in Figure~\ref{fig:dedupflow} (a),
when  a snapshot of a plain virtual disk file is being created, we first check the dirty bitmap array of
this disk file  to see which segments are modified. If a segment is not modified since last snapshot, 
it's data pointer in the recipe of the  parent snapshot  can be directly copied into 
current snapshot recipe (shown as the shadow area in Figure~\ref{fig:dedupflow} (b)).

\item {\em Block level checkup.}
As shown in Figure~\ref{fig:dedupflow} (b),
for each dirty segment, we divide it into variable-sized blocks,
and compare their signatures with  the corresponding segment recipe in the previous snapshot version (called parent
snapshot). 
For any duplicated block, we copy the data pointer directly from the parent segment recipe. 
\item {\em CDS checkup.} For the remaining  content blocks whose duplicate status is unknown,
Figure~\ref{fig:dedupflow} (d)
shows  a further check to compare  them with  the cached signatures in the CDS by querying
the CDS hash index. If there is a match, the corresponding data pointer from the CDS index is
copied into the segment recipe. 
\item {\em Write new snapshot blocks :}
We continue the previous step and 
if a data block cannot be found in the CDS index, this block is considered to be a new block
and such a block is to be saved in the snapshot block store and  the returned data pointer is
saved in the  segment recipe.
\item {\em Save recipes.} Finally the  segment recipes are saved in the  snapshot block store also.
 After all segment recipes are saved, the snapshot recipe is complete and can be saved finally.
\end{enumerate}

If there is no parent snapshot available, which happens when a VM creates its first snapshot, 
only CDS-based checkup will be conducted. 
Most of the cross-VM duplication, such as OS related data and popular software data, is eliminated
at this stage. Later snapshot will very likely find these data are not changed and simply copy the data pointers from parent snapshot.
%This is important because most of the cross-VM duplication, such as OS related data and popular software data, is eliminated
%at this stage. Later snapshot will very likely find these data are not changed and simply copy the data pointers from parent snapshot.

>>>>

\begin{figure}[htbp]
  \centering
  %\epsfig{file=images/arch.eps, height=2in, width=2.66in}
  \epsfig{file=images/arch.eps, width=3.9in}
  \caption{Snapshot backup architecture of each node.}
  \label{fig:arch}
\end{figure}

@@

%\begin{figure}[htbp]
%  \centering
%  %\epsfig{file=images/dedup_process.eps, height=2in, width=2.66in}
%  \epsfig{file=images/dedup_process.eps,  width=3.2in}
%  \caption{An example  of multi-level deduplication process.}
%  \label{fig:arch}
%\end{figure}
\begin{figure}[htbp]
  \centering
  %\epsfig{file=images/dedup_process.eps, height=2in, width=2.66in}
  \epsfig{file=images/snapshot_representation.eps,  width=3.8in}
  \caption{An example of snapshot representation.}
  \label{fig:snapshot}
\end{figure}

@@

In Aliyun's VM cloud, each VM explicitly maintains  one OS disk, plus one or more data disks.
During VM's creation, its OS disk is directly copied from user's chosen base image.
Given the separation of OS disks and data disks, we study  their characteristics separately.
We expect that data related to OS and popular software installations are not frequently
modified or deleted, to facilitate analysis we call them \emph{OS-related} data, 
and the rest of data, either from OS or data disks, are called \emph{user-related} data.
%base image data as a hint.Through users may change configurations, install software, or write user data into OS disk,
%Thus most of content blocks for the OS related snapshots  shall keep unchanged.
%This is verified in  Section~\ref{sect:exper}.
We have studied the popularity of common blocks in the OS and data disks from a dataset
containing over 1,000 VMs, taking their first snapshots to watch the cross-VM duplication pattern 
(scale of OS disk sampling is smaller due to performance impact to user VMs).
Figure \ref{fig:zipf-data} shows the duplicate count for unique data blocks sorted by their ranking in 
terms of the duplication count. $Y$ axis is the popularity of a data block in a log scale 
measured its duplicate count among snapshots. $X$ axis is the identification of data blocks in a log scale
sorted by their duplicate rank.  The rank number 1 is the block with the highest number of duplicates.
These two curves exhibit that the popularity of common blocks partially follows a Zipf-like distribution.
%$Y$ axis is the popularity of an OS block in a log scale 
%measured its duplicate count among snapshots. $X$ axis is the identification of OS blocks in a log scale
%sorted by their duplicate rank.  
%For the top ranked blocks, there is a flat line in terms of duplicate counts. That
%is because there are a large number of OS blocks which have appeared in all copies of such OS releases.

\begin{figure}[htbp]
\centering
\epsfig{file=images/vector.eps, width=3.8in}
%\epsfig{file=images/log-log.disk.eps, width=3in}

@@

%%Our deduplication process is divided into three levels, at each level, we eliminate the most of duplicate data with available knowledge, preventing them from going further because deduplication at deeper level is more expensive.
%
\begin{figure}
  \centering
  \epsfig{file=images/dedup_flow1.eps, width=3.8in}
  \caption{Illustration of snapshot deduplication dataflow.}
  \label{fig:dedupflow}
\end{figure}

We illustrate the steps of 3-level deduplication in Figure~\ref{fig:dedupflow}, which can be summarized as 5 steps:
\begin{enumerate}
\item {\em Segment level checkup.}
As shown in Figure~\ref{fig:dedupflow} (a),
when  a snapshot of a plain virtual disk file is being created, we first check the dirty bitmap 
to see which segments are modified. If a segment is not modified since last snapshot, 
it's data pointer in the recipe of the  parent snapshot  can be directly copied into 
current snapshot recipe (shown as the shadow area in Figure~\ref{fig:dedupflow} (b)).

\item {\em Block level checkup.}
As shown in Figure~\ref{fig:dedupflow} (b),
for each dirty segment, we divide it into variable-sized blocks,
and compare their signatures with  the corresponding segment recipe in the previous snapshot (called parent
snapshot). 
For any duplicated block, we copy the data pointer directly from the parent segment recipe. 
\item {\em CDS checkup.} For the remaining  content blocks whose duplicate status is unknown,
Figure~\ref{fig:dedupflow} (d)
shows  a further check to compare  them with  the cached signatures in the CDS by querying
the CDS hash index. If there is a match, the corresponding data pointer from the CDS index is
copied into the segment recipe. 
\item {\em Write new snapshot blocks :}
If a data block cannot be found in the CDS index, this block is considered to be a new block
and such a block is to be saved in the snapshot store, the returned data pointer is
saved in the  segment recipe.
\item {\em Save recipes.} Finally the  segment recipes are saved in the  snapshot block store also.
 After all segment recipes are saved, the snapshot recipe is complete and can be saved.
\end{enumerate}

If there is no parent snapshot available, which happens when a VM creates its first snapshot, 
only CDS-based checkup will be conducted. 
Most of the cross-VM duplication, such as OS-related data, is eliminated
at this stage. 
%Later snapshot will very likely find these data are not changed and simply copy the data pointers from parent snapshot.
%This is important because most of the cross-VM duplication, such as OS related data and popular software data, is eliminated
%at this stage. Later snapshot will very likely find these data are not changed and simply copy the data pointers from parent snapshot.

### 2012-03-10 vm_snapshot_sim/2012eval.tex
small adjustment

An Aliyun cluster we target is over 1000 nodes with 16 cores and 48GB memory
and each node hosts 25 VMs.
We are running our deduplication/backup  service on 100 nodes.
Memory usage is about 150MB space per node during backup and
the CPU usage is very small during the experiments. 
Based on the data studied,  each VM has about  40GB of storage  data usage on average
and each of OS disk and data disk takes about 50\% of storage space.
The backup of VM snapshots is completed within two hours  every day,
and that translates to a backup throughput of 139GB per second, or 500TB per hour.
For each VM, the system keeps  10 automatically-backed snapshots in the storage while
a user may instruct extra snapshots to be saved.

@@

\begin{figure}
  \centering
  \epsfig{file=images/overall_effect.eps, width=2.8in}
  \caption{Impacts of 3-level deduplication. The height of each bar is the data size after 
deduplication divided by the original data size and the unit is percentage. }

@@

\begin{figure}
  \centering
 %\epsfig{file=images/os_cds_sim.eps, width=3in}
  \epsfig{file=images/3level_os.eps, width=3in}
  \caption{Impact of 3-level deduplication for OS releases.}
  \label{fig:oscds}
\end{figure}

@@

\comments{
\begin{figure}[htbp]
\centering
%\epsfig{file=images/log-log.disk.eps, height=2in, width=2.66in}
%\epsfig{file=images/log-log.disk.eps, width=3in}
\epsfig{file=images/datadisk.count_rank.eps, width=3in}
\caption{Duplicate count  of common data blocks in a log scale.}
\label{fig:zipf-data}
\end{figure}
Figure \ref{fig:zipf-data} shows the duplicate count  for different data blocks sorted by their ranking in 
terms of the duplication count. $Y$ axis is the popularity of a data block in a log scale 
measured its duplicate count among snapshots. $X$ axis is the identification of data blocks in a log scale
sorted by their duplicate rank.  The rank number  1  is the block with the highest number of duplicates.
The curve exhibits that the popularity of common data blocks partially follows a  Zipf-like distribution.

\begin{figure}
\centering
%\epsfig{file=images/log-log.35vmos.eps,  width=3in}
%\epsfig{file=images/35os.count_rank.eps, width=3in}
\epsfig{file=images/35vmos.count-rank.eps,width=3in}
\caption{ Duplicate count of  common OS blocks in a log scale.}
\label{fig:OSpopular}
\end{figure}
Figure \ref{fig:OSpopular} shows the duplicate count  for OS disk snapshot blocks sorted by their ranking.
$Y$ axis is the popularity of an OS block in a log scale 
measured its duplicate count among snapshots. $X$ axis is the identification of OS blocks in a log scale
sorted by their duplicate rank.  For the top ranked blocks, there is a flat line in terms of duplicate counts. That
is because there are a large number of OS blocks which have appear in all copies of such OS releases.

@@

\begin{figure}
\centering
\epsfig{file=images/ay41a_big.data_disk.cdf.eps, width=2.8in}
%\epsfig{file=images/cdf.disk.v4.eps, width=3in}
%\epsfig{file=images/datadisk.count_rank.eps, width=3in}
%\epsfig{file=images/35os.count_rank.eps, width=3in}

@@

\begin{figure}
\centering
\epsfig{file=images/os_subset.eps, height=2in, width=2.66in}
\caption{Percentage of completely common blocks among different VMs for the same OS release.}
\label{fig:OSunchanged}
\end{figure}

@@

\begin{figure}
  \centering
  \epsfig{file=images/uniquedata-saving.eps, width=2.8in}
  \caption{Relative ratio of space size compared to full deduplication when CDS size changes.}
  \label{fig:datacdssize}
\end{figure}

@@

\begin{figure}
  \centering
  \epsfig{file=images/cds_scale.0.7.eps, width=2.8in}
  \caption{The relative size ratio of  CDS over the data size. }
  \label{fig:datacds}
\end{figure}

>>>>

An Aliyun our target is to backup cluster with 1000 nodes
with 25 VMs on each.
We are running our deduplication/backup  service on 100 nodes.
Memory usage is about 150MB space per node during backup and
the CPU usage is very small during the experiments. 
Based on the data studied,  each VM has about  40GB of storage  data usage on average,
OS disk and data disk each takes about 50\% of storage space.
The backup of VM snapshots is completed within two hours  every day,
and that translates to a backup throughput of 139GB per second, or 500TB per hour.
For each VM, the system keeps 10 automatically-backed snapshots in the storage while
a user may instruct extra snapshots to be saved.

@@

\begin{figure}
  \centering
  \epsfig{file=images/overall_effect.eps, width=3.5in}
  \caption{Impacts of 3-level deduplication. The height of each bar is the data size after 
deduplication divided by the original data size and the unit is percentage. }

@@

\begin{figure}
  \centering
 %\epsfig{file=images/os_cds_sim.eps, width=3in}
  \epsfig{file=images/3level_os.eps, width=3.5in}
  \caption{Impact of 3-level deduplication for OS releases.}
  \label{fig:oscds}
\end{figure}

@@

\comments{
\begin{figure}[htbp]
\centering
%\epsfig{file=images/log-log.disk.eps, height=2in, width=2.66in}
%\epsfig{file=images/log-log.disk.eps, width=3in}
\epsfig{file=images/datadisk.count_rank.eps, width=3.5in}
\caption{Duplicate count  of common data blocks in a log scale.}
\label{fig:zipf-data}
\end{figure}
Figure \ref{fig:zipf-data} shows the duplicate count  for different data blocks sorted by their ranking in 
terms of the duplication count. $Y$ axis is the popularity of a data block in a log scale 
measured its duplicate count among snapshots. $X$ axis is the identification of data blocks in a log scale
sorted by their duplicate rank.  The rank number  1  is the block with the highest number of duplicates.
The curve exhibits that the popularity of common data blocks partially follows a  Zipf-like distribution.

\begin{figure}
\centering
%\epsfig{file=images/log-log.35vmos.eps,  width=3in}
%\epsfig{file=images/35os.count_rank.eps, width=3in}
\epsfig{file=images/35vmos.count-rank.eps,width=3.5in}
\caption{ Duplicate count of  common OS blocks in a log scale.}
\label{fig:OSpopular}
\end{figure}
Figure \ref{fig:OSpopular} shows the duplicate count  for OS disk snapshot blocks sorted by their ranking.
$Y$ axis is the popularity of an OS block in a log scale 
measured its duplicate count among snapshots. $X$ axis is the identification of OS blocks in a log scale
sorted by their duplicate rank.  For the top ranked blocks, there is a flat line in terms of duplicate counts. That
is because there are a large number of OS blocks which have appear in all copies of such OS releases.

@@

\begin{figure}
\centering
\epsfig{file=images/ay41a_big.data_disk.cdf.eps, width=3.5in}
%\epsfig{file=images/cdf.disk.v4.eps, width=3in}
%\epsfig{file=images/datadisk.count_rank.eps, width=3in}
%\epsfig{file=images/35os.count_rank.eps, width=3in}

@@

\begin{figure}
\centering
\epsfig{file=images/os_subset.eps, width=3.5in}
\caption{Percentage of completely common blocks among different VMs for the same OS release.}
\label{fig:OSunchanged}
\end{figure}

@@

\begin{figure}
  \centering
  \epsfig{file=images/uniquedata-saving.eps, width=3.5in}
  \caption{Relative ratio of space size compared to full deduplication when CDS size changes.}
  \label{fig:datacdssize}
\end{figure}

@@

\begin{figure}
  \centering
  \epsfig{file=images/cds_scale.0.7.eps, width=3.5in}
  \caption{The relative size ratio of  CDS over the data size. }
  \label{fig:datacds}
\end{figure}

### 2012-03-10 vm_snapshot_sim/2012intro.tex
small adjustment

%,extreme_binning09,sparseindex09
By observations on the VM snapshot data from production cloud, we found snapshot data duplication 
can be easily classified into two categories: \emph{inner-VM} and \emph{cross-VM}. Inner-VM duplication
exists between VM's snapshots, because the majority of data are unchanged during each backup period. 
On the other hand, Cross-VM duplication is mainly due to widely-used software and libraries: 
there are only two type of OSes (Linux and Windows), most users either uses MySQL or MS SQL Server as their database.
As the result, different VMs tend to backup large amount of highly similar data.

>>>>

%,extreme_binning09,sparseindex09
By observations on the VM snapshot data from production cloud, we found snapshot data duplication 
can be easily classified into two categories: \emph{inner-VM} and \emph{cross-VM}. Inner-VM duplication
exists between VM's snapshots, because the majority of data are unchanged during each backup period. 
On the other hand, Cross-VM duplication is mainly due to widely-used software and libraries such as Linux and MySQL.
As the result, different VMs tend to backup large amount of highly similar data.

### 2012-03-10 vm_snapshot_sim/main.tex
small adjustment

\documentclass[finalversion]{usetex-v1}
%\usepackage[top=1in, bottom=1in, left=1.25in, right=1.25in]{geometry}
\usepackage[colorlinks,linkcolor=red,anchorcolor=blue,citecolor=green,urlcolor=black]{hyperref}
\usepackage{epsfig}
%\usepackage{breakurl}
%% Define a new 'leo' style for the package that will use a smaller font.
\makeatletter
\def\url@leostyle{%
  \@ifundefined{selectfont}{\def\UrlFont{\sf}}{\def\UrlFont{\small\ttfamily}}}
\makeatother
%% Now actually use the newly defined style.
\urlstyle{leo}
%\linespread{1.2}
%\setlength{\parskip}{1ex}

@@

\begin{document}
%\title{Selective Deduplication for VM Snapshots in Cloud Storage}
\title{Multi-level Selective Deduplication for VM Snapshots in Cloud Storage}
%\title{Data Deduplication and Zipf-like Distribution in VM Cloud Storage}
\author{Wei Zhang$^{\star\dagger}$, Hong Tang$^\dagger$, Hao Jiang$^\dagger$, Tao Yang$^\star$, 
Xiaogang Li$^\dagger$, and Rachael Zeng$^\dagger$ \\
   {\normalsize $^\star$UC Santa Barbara}\\
   {\normalsize$^\dagger$Alibaba.com}
}

@@

	%\linespread{0.3} 
  \let\oldthebibliography=\thebibliography
  \let\endoldthebibliography=\endthebibliography
  \renewenvironment{thebibliography}[1]{%
    \begin{oldthebibliography}{#1}%
      \setlength{\parskip}{-0.02ex}%
      \setlength{\itemsep}{-0.02ex}%
      \setlength{\baselineskip}{-0.02ex}%

  }%
  {%
    \end{oldthebibliography}%
  }
{\small
\bibliographystyle{abbrv}
\bibliography{dedup,dedup1}
}
\end{document}

>>>>

\documentclass[conference]{IEEEtran}
%\usepackage[top=1in, bottom=1in, left=1.25in, right=1.25in]{geometry}
\usepackage[colorlinks,linkcolor=red,anchorcolor=blue,citecolor=green,urlcolor=black]{hyperref}
\usepackage{epsfig}
%\usepackage{breakurl}
%% Define a new 'leo' style for the package that will use a smaller font.
%\makeatletter
%\def\url@leostyle{%
%  \@ifundefined{selectfont}{\def\UrlFont{\sf}}{\def\UrlFont{\small\ttfamily}}}
%\makeatother
%% Now actually use the newly defined style.
%\urlstyle{leo}
%\linespread{1.2}
%\setlength{\parskip}{1ex}

@@

\begin{document}
%\title{Selective Deduplication for VM Snapshots in Cloud Storage}
\title{Multi-level Selective Deduplication for VM Snapshots in Cloud Storage}
%\title{Data Deduplication and Zipf-like Distribution in VM Cloud Storage}
\author{
\IEEEauthorblockN{Wei Zhang\IEEEauthorrefmark{1}\IEEEauthorrefmark{2}, Hong Tang\IEEEauthorrefmark{2}, Hao Jiang\IEEEauthorrefmark{2}, Tao Yang\IEEEauthorrefmark{1}, Xiaogang Li\IEEEauthorrefmark{2}, Rachael Zeng\IEEEauthorrefmark{2}}
\IEEEauthorblockA{\IEEEauthorrefmark{1}Dept. of Computer Science, UC Santa barbara. Email: \{wei, tyang\}@cs.ucsb.edu}
\IEEEauthorblockA{\IEEEauthorrefmark{2}Alibaba Inc. Email: \{hongtang, haojiang, xiaogang, rachael\}@alibaba-inc.com}
%Wei Zhang$^{\star\dagger}$, Hong Tang$^\dagger$, Hao Jiang$^\dagger$, Tao Yang$^\star$, 
%Xiaogang Li$^\dagger$, and Rachael Zeng$^\dagger$ \\
%   {\normalsize $^\star$UC Santa Barbara}\\
%   {\normalsize$^\dagger$Alibaba.com}
}

@@

	%\linespread{0.3} 
%  \let\oldthebibliography=\thebibliography
%  \let\endoldthebibliography=\endthebibliography
%  \renewenvironment{thebibliography}[1]{%
%    \begin{oldthebibliography}{#1}%
%      \setlength{\parskip}{-0.02ex}%
%      \setlength{\itemsep}{-0.02ex}%
%      \setlength{\baselineskip}{-0.02ex}%

%  }%
%  {%
%    \end{oldthebibliography}%
%  }
{\small
\bibliographystyle{abbrv}
\bibliography{dedup,dedup1}
}
\end{document}
